### 2019-11-10 cvpr_submission/introduction.tex
wip on intro

\section{Introduction}

Deep Learning~\cite{lecun2015deep}

An assumption of traditional machine learning methodologies is the training data and testing data are taken from the same domain, such that the input feature space and data distribution characteristics are the same. However, in some real-world machine learning scenarios, this assumption does not hold. There are cases where training data is expensive or difficult to collect.

Transfer learning is used to improve a learner from one domain by transferring information from a related domain~\cite{pan2009survey}.

There can be  different types of transfer learnings in deep learning,
most popular being

In Computer Vision:

It became a standard to pretrain an image encoder or feature detector on ImageNet~\cite{deng2009imagenet} which is image classification task, and transfer it to unrelated domains and applications, such as e.g. visual question answering in medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}

In Language:

@@

>>>>

\section{Introduction}
During recent year neural networks, being the core of the so-called Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  speech recognition~\cite{graves2013speech}, to image classification~\cite{krizhevsky2012imagenet} to object detection~\cite{redmon2016you} to question answering~\cite{weston2014memory} to machine translation~\cite{bahdanau2014neural}.
At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing data are sampled from the same domain, i.e. operating in the same input space and with similar data distribution characteristics.
However, in many real-world scenarios, this assumption does not hold and besides, as modern neural models often have  milions of trainable parameters (weights), their trainng reguires a vaist amount of data, which for some domains (e.g. medical) can be very expensive and/or extremely difficult to collect.
One of the widely accepted solutions for the mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique that enables improving of a model by transferring \emph{information} from one domain to the other.

%pan2009survey: we categorize transfer learning under three sub-settings: inductive transfer learning, transductive transfer learning and unsupervised transfer learning,

In Computer Vision, it became a standard to pretrain an image encoder (such as VGG~\cite{simonyan2014very}) on a large scale dataset (like ImageNet~\cite{deng2009imagenet}), and transfer its weights to unrelated domains and tasks, such as e.g. Visual Question Answering (VQA) in medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
The fact that such a transfer improves performance is quite fascinating taking into account that both domain (natural images vs medical or images with cars) and task (image classification vs VQA or image segmentation) change (inductive transfer learning according to the taxonomy from~\cite{pan2009survey}).

Similarly, NLP...

@@

Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa} is a new exciting problem domain, where the system is expected to answer questions expressed in natural language by taking into account the content of the image.
